Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-08-04 MS.tex
Heterogenity analysis

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).

@@

\section*{Introduction}\label{introduction}

The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring. An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

@@

\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR}
Tree growth is the increase in dimensions (i.e. diameter, height or mass) of an individual tree through time. While plant functional traits measurements are standardized across plant ontogeny, plant growth is commonly expressed differently according to the plant size/stage considered. Thus, mass and height are both used for smaller plants, whereas height and diamater are more convenient measures for larger tree. In addition, the growth increment (i.e. rate of change of a dimension per unit time) can be expressed in either absolute or relative terms. Relative growth rate (RGR, the change in a dimension per time interval relative to initial size) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc). According to the growth model, the correlation between trait and growth is predicted to revert according to the growth measurement used, for both SLA and seed mass (TABLE?). The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e. becomes negative for SLA, positive for SM).

@@

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

We focused on an initial list of 20 traits (Fig. \ref{Fig1}) which capture different aspects of plant species strategies. Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}. We used the literature snapshot to identify traits which i) were most likely to return a substantial number of articles , and ii) shared a large proportion of their literature list with other traits. The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in

\ref{TableA1}. According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on two traits: SLA and WD.

@@

Google Scholar database was searched using the range of Boolean search terms for SLA and WD. Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*). The keyword search in Google Scholar returns approx. 18900 papers. For comparison, with the same keyword search Web of Science returns 541 papers. Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies (starred references in bibliography).

The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Therefore, we stratified the data set into two subsets: one including exclusively interspecific studies under unstressed conditions ('ideal' dataset), and the other set including all studies ('complete' dataset). We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage). Finally, we weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).

@@

While it would be more appropriate to address plant size as a continous variable, the limited quantity of data available in the literature steered us to focus on plant size as a categorical variable (i.e. plant stages). The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e. seedling, juvenile, sapling, adult). They also reported plant size informations in diameter, height or age; generally the authors give the size of the smallest and the biggest plants species used in their analyses. While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories. Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, Fig. A1). Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig. A1). In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm). The distinctions between sapling-adult in age (around 5 yrs) and height (around 2 m), and between seedling-sapling in diameter (around 1cm) were less pronounced. We used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to ensure that these size/stage cutoffs match across the different size measurements (i.e. diameter, height and age, Fig. A2). For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m. Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diamter or height (see Fig. A2 c).

@@

We tested size/stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. A8). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. A9). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species, and under non-stressed conditions (n=176). A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. A7).
While we were mainly interested by the relationships between traits and growth across species, around 9 percent of the litterature reports a correlation measured within species. The number of correlations recorded is too few to test our hypotheses at within species level. Yet, a 'raw' dataset (n=263) including correlations across and within species and under both non-stressed and all conditions generated similar results to those reported across species exclusively (Fig. A6).

@@

We found 112 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. A3). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. A8 for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. A4). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. A9). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. A9).

@@

The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits. While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies. Meta-analysis allowed us to generalize about trait influences on growth using the literature already available on traits. Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.

@@

>>>>

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations). As an approximation of plants size, we analysed the shift in the correlations between growth and traits across plant stages.

@@

\section*{Introduction}\label{introduction}
Plant growth is an important aspect of ecosystem productivity
Plant species vary considerably in the growth rate they can achieve under favourable growing conditions (Grime and Hunt 1975; Shipley and Keddy 1988; Poorter and Retakes 1990; Lambers and Poorter 1992). This variation is important both because potential RGR is an important aspect of ecological performance, and because slow potential RGR is thought to be part of a nexus of adaptations to unfavourable growing conditions (e.g. Grime et al. 1988; Reich et al. 1992; Chapin et al. 1993; Aerts and van der Pijl 1993; van der Werf et al. 1993).

The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring. An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR, the change in a mass/height or diamater per time interval relative to initial size) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into its components (see equation X in Appendix 1) showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

@@

\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR}
Tree growth is the increase in dimensions (i.e. diameter, height or mass) of an individual tree through time. While plant functional traits measurements are standardized across plant ontogeny, plant growth is commonly expressed differently according to the plant size/stage considered. Thus, mass and height are both used for smaller plants, whereas height and diamater are more convenient measures for larger tree. In addition, the growth increment (i.e. rate of change of a dimension per unit time) can be expressed in either absolute or relative terms. Relative growth rate (RGR) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc). According to the growth model used here, the correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass. The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e. becomes negative for SLA, positive for SM).

@@

To test how general is the tendency for correlations between traits and growth rate to vary with plant size, we focused on an initial list of 20 traits (Fig. \ref{Fig1}). These traits have been selected because they capture different aspects of plant species strategies, and are commonly addressed in the functional traits litterature. Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement across species. We searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (''NAME'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''NAME'' was one of trait names listed in \ref{TableA1}. According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on SLA and WD.

@@

Google Scholar database was searched using the range of Boolean search terms for SLA and WD. Search terms were as follows: ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*). The keyword search in Google Scholar returns approx. 18900 papers. For comparison, with the same keyword search Web of Science returns 541 papers. Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 112 different studies (starred references in bibliography). The articles laid aside because they did not meet our criteria are listed in Appendix \ref{app:supp_info_files} in Supplementary material.

The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Therefore, we focused on correlation across species, and we stratified the data set into two subsets: one including exclusively studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset). We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage). Finally, we weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).

@@

We acknowledge that it would be better to address plant size as a continous variable, but the limited number of correlations available in the literature along plant size steered us to focus on plant stage as an approximation. 
The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e. seedling, juvenile, sapling, adult). They also reported plant size informations in diameter, height or age; generally the authors give the size of the smallest and the biggest plants species used in their analyses. While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories. Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, Fig. A1). Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig. A1). In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm). The distinctions between sapling-adult in age (around 5 yrs) and height (around 2 m), and between seedling-sapling in diameter (around 1cm) were less pronounced. We used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to ensure that these size/stage cutoffs match across the different size measurements (i.e. diameter, height and age, Fig. A2). For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m. Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diameter or height (see Fig. A2 c).

@@

We tested stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. A9). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value. Finally, we explored the temporal change im effect size, by testing the effect of year of publication within stage for each trait. In Table 2 in Appendix, we reported how and where (i.e in the main text and/or figures) we addressed the 14 methodological quality criteria for meta-analysis listed by Koricheva and Gurevitch (2014).

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species, and under non-stressed conditions (n=176). A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. \ref{Fig2}. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. A7).

@@

We found 112 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. A3). Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included. Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance, r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. A4). The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig. A8). Number of species used for each correlation ranged from 2 to 300 species with average 31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. A9). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. A9).

@@

The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits. While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies already available. Meta-analysis allowed us to generalize and help to reach a concensus about trait influences on growth. Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.

@@

\begin{table}[ht]
\centering
\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014)} 
\label{TableA2}
\vspace{0.5cm}
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Criteria & Addressed & \\
  \hline
Aarea & Photosynthetic rate per area & "photosynthetic rate per area" OR "rate of CO2 assimilation per area" OR "Aarea" OR "Amax" OR "photosynthetic capacity per area" \\
  Amass & Photosynthetic rate per mass & "photosynthetic rate per mass" OR "rate of CO2 assimilation per mass" OR "Amass" OR "Amax" \\
  Hmax & Maximum height & "potential height" OR "maximum height" OR "Hmax" \\
  Ks & Stem specific conductance & "Ks" OR "stem specific conductance" OR "stem hydraulic conductance" OR "sapwood conductance" \\
  LA & Leaf lamina area & "leaf length" OR "leaf lamina area" OR "leaf width" OR "leaf size" \\
  LAR & Leaf area ratio & "leaf area ratio" \\
  LMR & Leaf mass ratio & "leaf mass ratio" OR "leaf mass fraction" \\
  NARarea & Net assimilation rate per area &  "net assimilation rate per area" OR "rate of dry mass increament per area" OR "NARarea" OR "NAR" \\
  Narea & Leaf nitrogen content per area & "Narea" OR "nitrogen per area" OR "N/area" OR "leaf nitrogen content per area" OR "LNCarea" OR "leaf nitrogen content" \\
  NARmass & Net assimilation rate per mass &  "net assimilation rate per mass" OR "rate of dry mass increament per mass" OR "NARmass" OR "NAR" \\
  Nmass & Leaf nitrogen content per mass & "Nmass" OR "nitrogen per mass" OR "N/mass" OR "leaf nitrogen content per mass" OR "LNCmass" OR "leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & "Parea" OR "leaf P" OR  "leaf phosphorus content per area"  OR "leaf phosphorus content" \\
  Pmass & Leaf phosphorus content per mass & "Pmass" OR "leaf P" OR  "leaf phosphorus content per mass" OR "leaf phosphorus content" \\
  SA/LA & Sapwood area per leaf area & "sapwood area per leaf area" OR "huber value" OR "leaf area per sapwood area" \\
  Seed mass & Seed mass & "seed mass" OR "seed size" OR "seed volume" \\
  SLA & Specific Leaf Area & "leaf mass per area" OR "specific leaf area" OR "leaf construction cost" \\
  Thickness & Leaf thickness & "leaf thickness"  OR "leaf tissue density" \\
  Vessel density & Vessel density & "vessel density" OR "stem conduit density" \\
  Vessel size & Vessel area or diameter & "conduit area" OR "stem conduit area" OR "vessel diameter" OR "vessel size" OR "conduit size"   \\
  WD & Wood density & "wood density" OR"WD" OR "wood specific gravity" OR "stem density" OR "stem specific density" OR "SSD" \\
   \hline
\end{tabular}
\end{table}

% we conducted two types of analyses to assess the reliability of our meta-analysis. First, we estimated heterogeneity using a modified version of the heterogeneity statistic I2 (originally defined by Higgins & Thompson, 2002; see Supporting information for details). Heterogeneity estimates the consistency of the results obtained from published stud- ies used in our meta-analysis. A low level of heteroge- neity means that discrepancies among the effects reported by the original studies are satisfactorily explained solely by sampling errors and are not the result of different methodologies or species characteris- tics (Higgins & Thompson, 2002; Higgins et al., 2003; Cooper & Hedges, 2009). Second, we assessed our data set for signs of publication bias by visually inspecting funnel plots (Sterne et al., 2005) and also by conducting Egger’s regressions (Egger et al., 1997; Peters et al., 2006). We applied an Egger’s regression design, modi- fied for lnOR to data points consisting of the residuals of the effect sizes plus their measurement errors
% a 2012 THE AUTHORS. J. EVOL. BIOL. 25 (2012) 1911–1917
% JOURNAL OF EVOLUTIONARY BIOLOGY a 2012 EUROPEAN SOCIETY FOR EVOLUTIONARY BIOLOGY
% Meta-analysis of cost of parental care in birds 1913
% 1914 E. S. A. SANTOS AND S. NAKAGAWA
% (Peters et al., 2006; see Supporting information for details). If the intercept of the Egger’s regression is sig- nificantly different from zero, it is evidence of p
